An Improvement of Controlling Quality of \\Large Scale Water-Level Data in Thailand

### 2015-04-02 paper.tex
comment from lab meeting

\author{\IEEEauthorblockN{Nuttapon Pattanavijit}
\IEEEauthorblockA{
Department of Computer Engineering\\
Faculty of Engineering\\
Chulalongkorn University\\
Phayathai Road, Pathumwan\\
Bangkok, Thailand 10330\\
Email: nuttapon.p@student.chula.ac.th
}
\and
\IEEEauthorblockN{Peerapon Vateekul}
\IEEEauthorblockA{
Department of Computer Engineering\\
Faculty of Engineering\\
Chulalongkorn University\\
Phayathai Road, Pathumwan\\
Bangkok, Thailand 10330\\
Email: peerapon.v@chula.ac.th
}
\and
\IEEEauthorblockN{Kanoksri Sarinnapakorn}
\IEEEauthorblockA{
Hydro and Agro Informatics Institute\\
Ministry of Science and Technology\\
Thailand, 10400\\
Email: kanoksri@haii.or.th
}}

@@

\begin{abstract}
%\boldmath
Extremely change in precipitation level such as water level can cause severe damage. In order to acknowledge changes, Hydro and Agro Informatics Institute has installed telemetry system across Thailand to collect and analyze precipitation level. However, to use its data in researching, incorrect data must be filtered. In previous work, we successfully detect various problems in water level data accurately. Still, missing pattern algorithm and outliers algorithm proposed in the previous work have run-time complexity up to $O(n^2)$, which are not quite suitable for large-scale data. In this paper, we aim to improve these algorithms, mainly focus on run-time complexity. As a result, we can speed up the outlier algorithm to $O(n)$ and the missing pattern to $O(n \log{n})$. Moreover, compared with the previous work, we measure actual running time of our algorithms and found that they significantly help reduce the running time.

\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the journal you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals frown on math
% in the abstract anyway.

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Purus, Vehicula, Ullamcorper, Dolor, Sollicitudin
\end{IEEEkeywords}

@@

Thailand has faced many dreadful climate-related disaster including floods, droughts, and tropical cyclones. They have happened year after year and cause severe loss. For example, In 2011, seasonal flooding results in US\$ 45.7 billion damage to Thailand’s economy, which is 1.1\% of the country’s GDP [1]. Also, the climate-related disaster bring difficulties to agriculture and industry, which are backbones of Thailand economy.

To handle these disaster, the government established many organization to cooperatively counteract with it. One of the organization is Hydro and Agro Informatics Institute (HAII). HAII’s main focus is to research and utilize knowledge in agricultural and water resource management to confront the climate disaster [2].

@@

To filtered out incorrect data efficiently, our previous work called “Controlling Quality of Water-Level Data in Thailand” proposed algorithms to detect anomalies in water level data, which includes outliers, inhomogeneity, and missing pattern algorithm [5]. Example of anomaly data detected by these algorithms is illustrated in figure \ref{fig:example_outliers}, figure \ref{fig:example_inhomogeneity}, and figure \ref{fig:example_missingpattern}. However, when we implement this algorithm to use with real precipitation level data, a problem arise. Since HAII use `R` as a main programming languages for all data analytic tasks, implementing outliers and missing pattern algorithm may leads to $O(n^2)$ in complexity. This inefficiency is originated from two main points. First, The bottleneck of both algorithms is occurred from clustering algorithm. The previous work use \textit{DBSCAN} [6] as the clustering algorithm which have $O(n^2)$ complexity if it is a naive implementation and $O(n\log{n})$ if it is implemented using special data structures that support fast region query such as \textit{R*-Tree} or \textit{k-d Tree} , which seem to be much more complex. Second, Our last work is implemented in HAII using \texttt{R} library called \texttt{fpc} which contains \textit{DBSCAN} library that have $O(n^2)$ complexity [7]. Thus, the overall algorithms’ complexity become $O(n^2)$.

@@

This paper aim to propose an improvement in outliers and missing pattern algorithms for large-scale water level data. Our main goal is to refine both algorithm to be simple, yet expeditious, while bring out the same results as our previous work. We have reduce running time of outliers algorithm from $O(n^2)$ or $O(n \log{n})$, depends on data structures, to $O(n)$. Also, missing pattern is decresed from $O(n^2)$ or $O(n \log^2{n})$ to $O(n \log{n})$. This can be  done by imitating the clustering result with more simple and fast approach which we will discuss later. The experimental result revealed that our approach significantly cuts down the overall running time in large-scale data.

@@

@@

@@

Proposed in previous work, missing pattern is used to detect pattern of missing data. \textbf{\color{red}Add some conjunction sentencs here!} First, it convert water-level data into frequency domain, which count how many data is missing during each hour ($f_{0} ,f_{1}, \ldots, f_{23}$). Second, we use DBSCAN to analyze the frequency. If there are more than one cluster detected, there must be at least two hours having significantly different missing frequency $(f_{i})$. Then, we ... . Next, divided-and-conquer technique was applied to find missing pattern in subset of data. Last, we merge overlapped missing result together.

@@

%First, since the data was captured from a sensor, we can assume that at time $t$, there will be only one $d_{t}$. This fact implies that there is no need to search for adjacent point in two dimension. Also, the data is already sorted by time. So, searching for data points that have distance from $d_{t}$ less than $\epsilon$ can be done in linear time by looking forward and backward from $d_{t}$. In other words, we can try to increase $j$ then check the distance between $d_{t}$ and $d_{t+j}$ until the distance is greater than $\epsilon$. On the other hand, looking backward for distance between $d_{t}$ and $d_{t-i}$ can be done in the same way. We can say that finding $i_{max}$, $j_{max}$ for
%\[
%D = \{d_{t-i}, \ldots, d_{t}, \ldots, d_{t+j}\}
%\]
%
%where
%
%\[
%|d_{t-i} - d_{t}|\le\epsilon\textit{ and }|d_{t+j} - d_{t}|\le\epsilon
%\]
%can be done in linear time.

>>>>

\author{\IEEEauthorblockN{Nuttapon Pattanavijit, Peerapon Vateekul}
\IEEEauthorblockA{
Department of Computer Engineering\\
Faculty of Engineering, Chulalongkorn University\\
Phayathai Road, Pathumwan\\
Bangkok, Thailand, 10330\\
Email: {nuttapon.p@student.chula.ac.th, peerapon.v@chula.ac.th}
}
\and
\IEEEauthorblockN{Kanoksri Sarinnapakorn}
\IEEEauthorblockA{
Hydro and Agro Informatics Institute\\
Ministry of Science and Technology\\
Thailand, 10400\\
Email: kanoksri@haii.or.th
}}

@@

\begin{abstract}
%\boldmath
Extremely change in precipitation level such as water level can cause severe damage. In order to acknowledge changes, Hydro and Agro Informatics Institute has installed telemetry system across Thailand to collect and analyze precipitation level. However, to use its data in researching, incorrect data must be filtered. In previous work, we successfully detect various problems in water level data accurately. Still, outliers detection algorithm  and missing pattern proposed in the previous work still room for improvement in terms of running time and ease of implementation. In this paper, we propose to improve the clustering algorithm in the previous work ...

Still, outliers algorithm proposed in the previous work has  run-time complexity from $O(n\log{n})$ up to $O(n^2)$, which are not quite suitable for large-scale data. Missing pattern algorithm has $O(n\log{n})$ complexity but it use complicated data structure. In this paper, we aim to improve these algorithms. As a result, we can speed up the outlier algorithm to $O(n)$ and hold the missing pattern's complexity at $O(n \log{n})$ but with simpler algorithm. Moreover, compared with the previous work, we measure actual running time of our algorithms and found that they significantly help reduce the running time {\color{red} remove math symbol from abstract.}.

\end{abstract}

\begin{IEEEkeywords}
\color{red} Do, not, forget, to, insert, keyword, here
\end{IEEEkeywords}

@@

Thailand has faced many dreadful climate-related disaster including floods, droughts, and tropical cyclones. They have happened year after year and cause severe loss. For example, In 2011, seasonal flooding results in US\$ 45.7 billion damage to Thailand’s economy, which is 1.1\% of the country’s GDP [1]. Also, the climate-related disaster bring difficulties to agriculture and industry, which are backbones of Thailand economy. To handle these disaster, the government established many organization to cooperatively counteract with it. One of the organization is Hydro and Agro Informatics Institute (HAII). HAII’s main focus is to research and utilize knowledge in agricultural and water resource management to confront the climate disaster [2].

@@

To filtered out incorrect data efficiently, our previous work [5] proposed algorithms to detect anomalies in water level data, which includes outliers, inhomogeneity, and missing pattern algorithm. Example of anomaly data detected by these algorithms is illustrated in figure \ref{fig:example_outliers}, figure \ref{fig:example_inhomogeneity}, and figure \ref{fig:example_missingpattern}. {\color{red} However, when we implement this algorithm to use with real precipitation level data, a problem arise. Since HAII use `R` as a main programming languages for all data analytic tasks, implementing outliers and missing pattern algorithm may leads to $O(n^2)$ in complexity. This inefficiency is originated from two main points. First, The bottleneck of both algorithms is occurred from clustering algorithm. The previous work use \textit{DBSCAN} [6] as the clustering algorithm which have $O(n^2)$ complexity if it is a naive implementation and $O(n\log{n})$ if it is implemented using special data structures that support fast region query such as \textit{R*-Tree} or \textit{k-d Tree} , which seem to be much more complex. Second, Our last work is implemented in HAII using \texttt{R} library called \texttt{fpc} which contains \textit{DBSCAN} library that have $O(n^2)$ complexity [7]. Thus, the overall algorithms’ complexity become $O(n^2)$.}

In the previous version, it require a high algorithm's complexity due to DBSCAN ($<$--- complex), so the implementation time is also high as well.

Although same compx, dbscam much more complex. real runtime take more time.

1. compx higher (OL)
2. more complicated
3. runtime higher even though same compx.

------------

\textbf{\color{red} Important!}
In this paper, we propose to improve the clustering algorithm in the previous work for water-level data. A linear clustering algorithm is invented and used to replace DBSCAN clustering.

-------------

{\color{blue}
	New Paragraph Here

	However, when we implement this algorithm to use with real precipitation level, we have found some interesting facts. According to the previous paper, both outliers detection algorithm and missing pattern algorithm depend on \textit{DBSCAN} [6] as the clustering algorithm. For outliers algorithm, \textit{DBSCAN} have $O(n^2)$ complexity if it is a naive implementation and $O(n\log{n})$ if it is implemented using special data structures that support fast region query such as \textit{R*-Tree} or \textit{k-d Tree} , which seem to be much more complex. 
}

@@

{\color{red}
This paper proposes an improvement in outliers and missing pattern algorithms for large-scale water level data. Our main goal is to refine both algorithms to be simple, yet expeditious, while bring out the same results as our previous work. We have reduce running time of outliers algorithm from $O(n^2)$ or $O(n \log{n})$, depends on data structures, to $O(n)$. Also, missing pattern is decresed from $O(n^2)$ or $O(n \log^2{n})$ to $O(n \log{n})$. This can be  done by imitating the clustering result with more simple and fast approach which we will discuss later. The experimental result revealed that our approach significantly cuts down the overall running time in large-scale data.
}

----------

1. speed 2.simple 3.accuracy

remove dbscan and replace with something

1. what you want to do 2. how you do 3. what is the result
replace with our proposed linear search method

----------

@@

---------

Say That $O(n^2)$ is too slow

Can be moved into Introduction

Change Figure to Fig.

---------

@@

----------

Say that previous work never analyze complexity

Topic name can be change to mention analyzing complexity

----------

@@

\textbf{\color{red} This is disaster, Fix the complexity analysis}

Proposed in previous work, missing pattern is used to detect pattern of missing data. \textbf{\color{red}Add some conjunction sentencs here!} First, it convert water-level data into frequency domain, which count how many data is missing during each hour ($f_{0} ,f_{1}, \ldots, f_{23}$). Second, we use DBSCAN to analyze the frequency. If there are more than one cluster detected, there must be at least two hours having significantly different missing frequency $(f_{i})$. Then, we \textbf{\color{red} insert missing sentence here!} . Next, divided-and-conquer technique was applied to find missing pattern in subset of data. Last, we merge overlapped missing result together.

@@
